---
title: "K-fold Cross Validation in R Programming"
author: "Anuradha Perera"
date: "2026-08-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(caret)
library(randomForest)
library(ISLR)
library(lattice)
library(tidyverse)
library(datarium)
```

### Implementation of K-Fold Cross-Validation on Classification

#### 1. Installing Required Packages


#### 2. Loading Libraries and Dataset

```{r}
data("Smarket")
dataset <- na.omit(Smarket)  
dataset <- dataset %>% select(-Year)
```

#### 3. Exploring the dataset

```{r}
glimpse(dataset)
```

#### 4. Training model using 10-fold cross-validation

We are using Random Forest algorithm with 10-fold CV to train the classification model.

```{r}
set.seed(123)
train_control <- trainControl(method = "cv", number = 10, sampling = "up")

model_rf <- train(
  Direction ~ ., 
  data = dataset,
  method = "rf", 
  trControl = train_control
)
```

#### 5. Evaluating Model Performance

using confusion matrix

```{r}
print(model_rf)
```
### Implementation the K-fold Technique on Regression

#### 1. Installing Required Packages

#### 2. Loading and Inspecting the Dataset

```{r}
data("marketing")
head(marketing)
```


#### 3. Training the Model with 10-Fold Cross-Validation

```{r}
set.seed(125)

train_control <- trainControl(method = "cv", number = 10)

model <- train(sales ~ ., data = marketing,
               method = "lm",
               trControl = train_control)

print(model)
```

